Data Processing

### 2020-01-25 analysis/data_processing.Rmd
update visualizations

ggplot() +
  geom_hline(yintercept = .5, lty=2, size = 1)+
  geom_line(data = samples, aes(x = age, y = y, group = sample), size = .025, col = "grey")+
  geom_line(data = maps, aes(x = age, y = y), size = 1)+
  geom_jitter(data = p_data,aes(x = age, y= correct), width = .00, height = .01, alpha = .2)+
  geom_pointrange(data = p_data2, aes(x = subage+.5, y = mean, ymin = ci_lower, ymax = ci_upper),size = .5, position = position_dodge(width = .2), pch = 5, col = "#6866cc")+
  labs(x="Age",y="Proportion correct")+
  facet_wrap(~task, nrow = 2)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F, col = F)+
  coord_fixed(ratio = 2)
```

>>>>

ggplot() +
  geom_hline(yintercept = .5, lty=2, size = 1)+
  geom_line(data = samples, aes(x = age, y = y, group = sample), size = .025, col = "grey")+
  geom_line(data = maps, aes(x = age, y = y), size = 1)+
  geom_jitter(data = p_data,aes(x = age, y= correct), width = .00, height = .01, alpha = .2)+
  geom_pointrange(data = p_data2, aes(x = subage+.5, y = mean, ymin = ci_lower, ymax = ci_upper),size = .5, position = position_dodge(width = .2), pch = 5, col = "#6866cc")+
  labs(x="Age",y="Proportion correct")+
  facet_wrap(~task, nrow = 1)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F, col = F)+
  coord_fixed(ratio = 2)+
  ggsave("../graphs/task_results.png", width = 10, height = 2.5, scale = 1.2)
```

# Visualizing predictor for age

library(ggridges)

x <- bind_rows(
  posterior_samples(card_sorting_model1, "^b")%>%
  select(b_age)%>%
  mutate(task = "1 card_sorting",
         ci = ifelse(b_age < fixef(card_sorting_model1)[2,3] | b_age > fixef(card_sorting_model1)[2,4], 1,2)),
  posterior_samples(inf_model1, "^b")%>%
  select(b_age)%>%
  mutate(task = "4 informativeness",
         ci = ifelse(b_age < fixef(inf_model1)[2,3] | b_age > fixef(inf_model1)[2,4], 1,2)),
  posterior_samples(nov_model1, "^b")%>%
  select(b_z_age)%>%
  rename(b_age = b_z_age)%>%
  mutate(task = "2 novelty",
         ci = ifelse(b_age < fixef(nov_model1)[2,3] | b_age > fixef(nov_model1)[2,4], 1,2)),
  posterior_samples(me_model1, "^b")%>%
  select(b_z_age)%>%
  rename(b_age = b_z_age)%>%
  mutate(task = "3 mutual_exclusivity",
         ci = ifelse(b_age < fixef(me_model1)[2,3] | b_age > fixef(me_model1)[2,4], 1,2))
)

ggplot(x, aes(x = b_age, y = task, fill = factor(stat(quantile))))+
  geom_vline(xintercept = 0, col = "grey", lty = 2)+
  stat_density_ridges(
    geom = "density_ridges_gradient",
    calc_ecdf = TRUE,
    quantiles = c(0.025, 0.975)
  ) +
  scale_fill_manual(values = c("white", "lightblue", "white"))+ 
  guides(fill = F)+
  xlim(-10,20)+
  theme_few()
